Test data

### 2022-07-21 Shiny/Test/Flexdashboard rows.Rmd
Plotly madness (fixing currency subtitle).

  # Creating KPI_admin value
  KPI_admin <- reactive({
    exceldata() |>
      mutate(
        KPI_admin =
          str_c( # Using str_c() to concatenate value and % sign
            format( # shortening(lengthening) the resulting value
              # calculating the value
              (expenses_administrative / (expenses_program_services +
                                            expenses_administrative +
                                            expenses_fundraising +
                                            expenses_other) * 100),
              digits = 3
            ), "%"
          )
      ) |>
      filter(year == max(year)) |> # selecting latest available year
      select(KPI_admin) |> # dropping all other variables
      str_flatten() # turning into a single string
  })

@@

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

  # Creating value box for fundraising ROI
  # Unsure about colour levels
  output$KPI_box_fundraising <- renderValueBox({
    valueBox(
      # shortening(lengthening) the value with format()
      # Using str_c() to concatenate value and % sign;
      value = str_c(format(KPI_fundraising_num(), digits = 3), "%"),
      caption = "Fundraising ROI",

@@

  output$KPI_box4 <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "info",
      color = "info",
      icon = "fas fa-skull-crossbones"
    )
  })

  output$KPI_box5 <- renderValueBox({
    valueBox(
      value = KPI_admin(),
      caption = "warning",
      color = "warning",
      icon = "fas fa-battery-empty"
    )
  })

  #---- Plots --------------------------------------------------------------------    
  #----CEO compensation-----------------------------------------------------------
  CEO_plot <- reactive({
    htmldata() |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      scale_y_continuous(
        # Checking for uniform currency code
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
          # Using the currency code if uniform
          label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
          # alternative prefix if multiple currencies in the data
          label_dollar(prefix = "? ")
        )
      ) +
      # pretty colours
      scale_fill_met_d("Troy") +
      labs(
        x = "Year", y = "Total compensation", title = "Annual CEO compensation",
        # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
          "",
          "Note: not all values are denominated in the same currency"
        )
      )
  })

  # Creating plotly output
  output$CEO_plotly <- renderPlotly(
    ggplotly(CEO_plot())
  )

  #----Annual result---------------------------------------------
  arsresultat_plot <- reactive({
    htmldata() |>
      ggplot(aes(year, arsresultat, fill = annual_profit)) +
      geom_col() +
      scale_y_continuous(
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
          # Using the currency code if uniform
          label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
          # alternative prefix if multiple currencies in the data
          label_dollar(prefix = "? ")
        )
      ) +
      # slightly nicer colours + ensuring positive values are always green
      scale_fill_met_d("Tsimshian",
        direction =
          ifelse(mean(htmldata()$annual_profit,
            na.rm = TRUE
          ) == 1, -1, 1)
      ) +
      theme(legend.position = "none") +
      labs(
        x = "Year", y = "", title = "Annual result (in thousands)",
        # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
          "",
          "Note: not all values are denominated in the same currency"
        )
      )
  })

  output$arsresultat_plotly <- renderPlotly(
    ggplotly(arsresultat_plot())
  )
  #----Balance--------------------------------------------------------------------    
  balance_plot <- reactive({
  htmldata() |>
    ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
    geom_col() +
    scale_y_continuous(
      labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
        # Using the currency code if uniform
        label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
        # alternative prefix if multiple currencies in the data
        label_dollar(prefix = "? ")
      )
    ) +
    # slightly nicer colours + ensuring positive values are always green
    scale_fill_met_d("Tsimshian",
      direction = ifelse(
        mean(htmldata()$balance_positive,
          na.rm = TRUE
        ) == 1, -1, 1
      )
    ) +
    theme(legend.position = "none") +
    labs(
      x = "Year", y = "", title = "Balance (in thousands)",
      # Checking again for currency; including warning if not uniform
      subtitle =
        ifelse(length(unique(htmldata()$valutakode)) == 1,
          "",
          "Note: not all values are denominated in the same currency"
        )
    )
})

  output$balance_plotly <- renderPlotly(
    ggplotly(balance_plot())
  )

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |> 
  transmute(
    Year = as.factor(year),
    Other = expenses_other,
    Administrative = expenses_administrative,
    Fundraising = expenses_fundraising,
    `Program services` = expenses_program_services
  ) |> 
  pivot_longer(c(Other:`Program services`), names_to = "Expenses") |> 
  mutate(
    Expenses = ordered(Expenses, levels =
                         c("Program services", "Administrative",
                         "Fundraising", "Other")) 
  ) |> 
  ggplot(aes(Year, value, fill = Expenses)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = label_dollar()) +
  scale_fill_met_d("Troy")
  })

  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot())
  )
})
```

```{r functions, include=FALSE}
# Function to read html file
read_proff8 <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    select( # removing empty column
      REGNSKAPSPERIODE:all_of(start)
    ) |> # using all_of()
    mutate( # removing whitespace
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
    filter( # removing duplicate rows
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    pivot_longer( # tidying data
      all_of(end):all_of(start),
      names_to = "year"
    ) |> # using all_of()
    mutate( # changing to real NAs and turning years into numbers
      value = na_if(value, "-"),
      year = as.integer(year),
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    fill( # filling the currency column
      valutakode,
      .direction = "updown"
    ) |>
    filter( # removing dates and redundant currency
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( # removing whitespace in numbers
      value = str_replace_all(value, "\\s", ""),
      value = as.numeric(value),
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    distinct() |> # removing any remaining duplicate rows
    pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    clean_names() |> # tidying names
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> # removing headings
    rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    arrange(desc(year)) # arranging by year
}

# Function to read Excel file
widen_excel <- function(file) {
  read_excel(file) |>
    unite( # uniting Category and Name to deal with multiple 'Other'
      entry, c(Category, Name),
      sep = "_"
    ) |>
    select(-`Sub-category`) |> # deleting Sub-category
    # pivoting
    pivot_wider(names_from = entry, values_from = Value) |>
    clean_names() # cleaning names
}
```

>>>>

  # Creating KPI_admin value
  KPI_admin_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      # Calculating the value as a percentage; removing all other
      transmute(
        KPI_admin = expenses_administrative / (expenses_program_services +
          expenses_administrative +
          expenses_fundraising +
          expenses_other) * 100
      ) |>
      # just want the single number
      pull()
  })

@@

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

  # Creating value box for fundraising ROI
  # Unsure about colour levels
  output$KPI_box_fundraising <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_fundraising_num()),
      caption = "Fundraising ROI",

@@

  output$KPI_box4 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

  output$KPI_box5 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = met.brewer("Wissing", n = 1),
      icon = "fa-random"
    )
  })

  #---- Plots --------------------------------------------------------------------    
  #----CEO compensation-----------------------------------------------------------
  CEO_plot <- reactive({
    htmldata() |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      scale_y_continuous(
        # Checking for uniform currency code
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
          # Using the currency code if uniform
          label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
          # alternative prefix if multiple currencies in the data
          label_dollar(prefix = "? ")
        )
      ) +
      # pretty colours
      scale_fill_met_d("Troy") +
      labs(
        x = "", y = "Total compensation", title = "CEO compensation"
      )
  })

  # Creating plotly output
  output$CEO_plotly <- renderPlotly(
    ggplotly(CEO_plot()) |>
      layout(
        annotations =
          list(
            x = 1, y = -0.1, text = currency_caption(),
            showarrow = F, xref = "paper", yref = "paper",
            xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
            font = list(size = 11)
          )
      )
  )

  #----Annual result---------------------------------------------
  arsresultat_plot <- reactive({
    htmldata() |>
      ggplot(aes(year, arsresultat, fill = annual_profit)) +
      geom_col() +
      currency_scale() +
      # slightly nicer colours + ensuring positive values are always green
      scale_fill_met_d("Tsimshian",
        direction =
          ifelse(mean(htmldata()$annual_profit,
            na.rm = TRUE
          ) == 1, -1, 1)
      ) +
      theme(legend.position = "none") +
      labs(
        x = "", y = "", title = "Annual result (in thousands)"
      )
  })

  output$arsresultat_plotly <- renderPlotly(
    ggplotly(arsresultat_plot()) |>
      layout(
        annotations =
          list(
            x = 1, y = -0.1, text = currency_caption(),
            showarrow = F, xref = "paper", yref = "paper",
            xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
            font = list(size = 11)
          )
      )
  )
  #----Balance--------------------------------------------------------------------    
  balance_plot <- reactive({
    htmldata() |>
      ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
      geom_col() +
      currency_scale() +
      # slightly nicer colours + ensuring positive values are always green
      scale_fill_met_d("Tsimshian",
        direction = ifelse(
          mean(htmldata()$balance_positive,
            na.rm = TRUE
          ) == 1, -1, 1
        )
      ) +
      theme(legend.position = "none") +
      labs(
        x = "", y = "", title = "Balance (in thousands)",
      )
  })

  output$balance_plotly <- renderPlotly(
    ggplotly(balance_plot()) |>
      layout(
        annotations =
          list(
            x = 1, y = -0.1, text = currency_caption(),
            showarrow = F, xref = "paper", yref = "paper",
            xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
            font = list(size = 11)
          )
      )
  )

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      mutate(
        Expenses = ordered(Expenses,
          levels =
            c(
              "Program services", "Administrative",
              "Fundraising", "Other"
            )
        )
      ) |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      coord_flip() +
      currency_scale() +
      scale_fill_met_d("Troy") +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot()) |>
      layout(
        annotations =
          list(
            x = 1, y = -0.1, text = currency_caption(),
            showarrow = F, xref = "paper", yref = "paper",
            xanchor = "right", yanchor = "auto", xshift = 0, yshift = 0,
            font = list(size = 11)
          )
      )
  )

  #----Reactive functions-------------------------------
  # Reactive function to check for currency and use currency code or ?
  currency_scale <- reactive({
    scale_y_continuous(
      # Checking for uniform currency code
      labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
        # Using the currency code if uniform
        label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
        # alternative prefix if multiple currencies in the data
        label_dollar(prefix = "? ")
      )
    )
  })

  # Reactive function to create currency caption
  currency_caption <- reactive({
    if (length(unique(htmldata()$valutakode)) == 1) {
      ""
    } else {
      "Note: not all values are denominated in the same currency"
    }
  })
})

```{r non-reactive functions, include=FALSE}
# Function to read html file
read_proff8 <- function(file, start, end) {
  read_html(file, encoding = "UTF-8") |>
    html_node("#inner-frame") |>
    html_table() |>
    select( # removing empty column
      REGNSKAPSPERIODE:all_of(start)
    ) |> # using all_of()
    mutate( # removing whitespace
      REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
    ) |>
    filter( # removing duplicate table - no idea why it's necessary
      !row_number() > 176
    ) |>
    filter( # removing duplicate rows
      !grepl("Lukk", REGNSKAPSPERIODE)
    ) |>
    pivot_longer( # tidying data
      all_of(end):all_of(start),
      names_to = "year"
    ) |> # using all_of()
    mutate( # changing to real NAs and turning years into numbers
      value = na_if(value, "-"),
      year = as.integer(year),
      valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
    ) |>
    fill( # filling the currency column
      valutakode,
      .direction = "updown"
    ) |>
    filter( # removing dates and redundant currency
      REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
        REGNSKAPSPERIODE != "Valutakode"
    ) |>
    mutate( # removing whitespace in numbers
      value = str_replace_all(value, "\\s", ""),
      value = as.numeric(value),
      value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
    ) |>
    distinct() |> # removing any remaining duplicate rows
    pivot_wider( # pivoting
      names_from = REGNSKAPSPERIODE, values_from = value
    ) |>
    clean_names() |> # tidying names
    select(
      -lederlonn_i_hele_1000,
      -resultatregnskap_i_hele_1000,
      -balanseregnskap_i_hele_1000
    ) |> # removing headings
    rename( # making it clear what lonn refers to
      lederlonn = lonn
    ) |>
    # Creating new variables for plots
    mutate(
      annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
      balance_positive = ifelse(sum_egenkapital_og_gjeld >= 0, TRUE, FALSE)
    ) |>
    arrange(desc(year)) # arranging by year
}

# Function to read Excel file
widen_excel <- function(file) {
  read_excel(file) |>
    unite( # uniting Category and Name to deal with multiple 'Other'
      entry, c(Category, Name),
      sep = "_"
    ) |>
    select(-`Sub-category`) |> # deleting Sub-category
    # pivoting
    pivot_wider(names_from = entry, values_from = Value) |>
    clean_names() # cleaning names
}

# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable){
  if (variable == 0 | is.na(variable)){
    NA
  } else {
    str_c(format(variable, digits = 3), "%")
  }
}

### 2022-07-21 Shiny/Test/Test data.Rmd
Plotly madness (fixing currency subtitle).

read_proff_tidied <- function(file, start, end) {
    read_html(file, encoding = "UTF-8") |>
        html_node("#inner-frame") |>
        html_table() |>
        # removing empty column
    select(REGNSKAPSPERIODE:all_of(start)) |>
        # removing whitespace
    mutate(REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)) |>
        # removing duplicate table - no idea why it's necessary
    filter(!row_number() > 176) |>
        # removing duplicate rows
    filter(!grepl("Lukk", REGNSKAPSPERIODE)) |>
        # tidying data
    pivot_longer(
        all_of(end):all_of(start),
        names_to = "year"
    ) |>
        # changing to real NAs and turning years into numbers picking
        # out the currency
    mutate(
        value = na_if(value, "-"),
        year = as.integer(year),
        valutakode = ifelse(
            REGNSKAPSPERIODE == "Valutakode", value,
            NA
        )
    ) |>
        # filling the currency column
    fill(valutakode, .direction = "updown") |>
        # removing dates and redundant currency
    filter(
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE !=
            "Startdato" & REGNSKAPSPERIODE != "Valutakode"
    ) |>
        # removing white space in numbers and removing years as numbers
    mutate(
        value = str_replace_all(value, "\\s", ""),
        value = as.numeric(value),
        value = ifelse(
            grepl("i hele 1000", REGNSKAPSPERIODE),
            NA, value
        )
    ) |>
        # removing any remaining duplicate rows
    distinct() |>
        # pivoting
    pivot_wider(names_from = REGNSKAPSPERIODE, values_from = value) |>
        # tidying names
    clean_names() |>
        # removing headings
    select(
        -lederlonn_i_hele_1000, -resultatregnskap_i_hele_1000,
        -balanseregnskap_i_hele_1000
    ) |>
        # making it clear what lonn refers to
    rename(lederlonn = lonn) |>
        # Creating new variables for plots
    mutate(
        annual_profit = ifelse(arsresultat >= 0, TRUE, FALSE),
        balance_positive = ifelse(
            sum_egenkapital_og_gjeld >= 0, TRUE,
            FALSE
        )
    ) |>
        # arranging by year
    arrange(desc(year))
}

@@

# New
kreft_html5 |> 
  select(
          year, lederlonn, leder_annen_godtgjorelse
         ) |> 
        # Compensation in ordinary numbers
        mutate(
          lederlonn = lederlonn * 1000,
          leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
        ) |> 
        # renaming for the purposes of the plot
        rename( 
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |> 
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        scale_y_continuous(
          # Checking for uniform currency code
        labels = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(kreft_html5$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
         ) +
        # pretty colours
        scale_fill_met_d("Troy") + 
        labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
kreft_html5 |> 
ggplot(aes(year, arsresultat, fill = annual_profit)) +
      geom_col() +
      scale_y_continuous(
        labels = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(kreft_html5$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
        ) +
        # slightly nicer colours + ensuring positive values are always green
      scale_fill_met_d("Tsimshian",
                   direction = ifelse(mean(kreft_html5$annual_profit, na.rm = TRUE) == 1,-1, 1)) +
      theme(legend.position = "none") +
      labs(x = "Year", y = "", title = "Annual result (in thousands)",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))

mean(kreft_html5$annual_profit)
kreft_html5$annual_profit
```

@@

ordinaert_p_met <- kreft_html |> 
  mutate(
    profit = ifelse(ordinaert_resultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, ordinaert_resultat, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  theme(legend.position = "none") +
  scale_fill_met_d("Tsimshian",
                   direction = ifelse(mean(kreft_html$ordinaert_resultat) == 1,-1, 1)) +
  theme(legend.position = "none") +
  labs(x = "", y = "")
ggplotly(ordinaert_p_met)
```

@@

kreft_html_with_variables |> 
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
  geom_col() +
  scale_y_continuous(
        labels = ifelse(length(unique(kreft_html_with_variables$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(kreft_html_with_variables$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
        ) +
  scale_fill_met_d("Tsimshian",
                   direction = ifelse(
                     mean(kreft_html_with_variables$balance_positive,
                          na.rm = TRUE) == 1,-1, 1)) +
  theme(legend.position = "none") +
  labs(x = "Year", y = "", title = "Balance (in thousands)",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(kreft_html_with_variables$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))

@@

kreft_excel |> mutate(
            KPI_admin =
              expenses_administrative / expenses_program_services *100) |> 
           filter(year == max(year)) |> 
          select(KPI_admin)
```

>>>>

@@

# New
kreft_html5 |> 
  select(
          year, lederlonn, leder_annen_godtgjorelse
         ) |> 
        # Compensation in ordinary numbers
        mutate(
          lederlonn = lederlonn * 1000,
          leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
        ) |> 
        # renaming for the purposes of the plot
        rename( 
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |> 
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        scale_y_continuous(
          # Checking for uniform currency code
        labels = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(kreft_html5$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
         ) +
        # pretty colours
        scale_fill_met_d("Troy") + 
        labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
testplot <- kreft_html5 |> 
ggplot(aes(year, arsresultat, fill = annual_profit)) +
      geom_col() +
      scale_y_continuous(
        labels = ifelse(length(unique(kreft_html5$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(kreft_html5$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
        ) +
        # slightly nicer colours + ensuring positive values are always green
      scale_fill_met_d("Tsimshian",
                   direction = ifelse(mean(kreft_html5$annual_profit, na.rm = TRUE) == 1,-1, 1)) +
      theme(legend.position = "none") +
      labs(x = "Year", y = "", title = "Annual result (in thousands)",
             # Checking again for currency; including warning if not uniform
        subtitle = "test")

testplot
ggplotly(testplot) |> layout(title = list(text = str_c('US State Population and Life Expectancy',
                                    '<br>',
                                    '<sup>',
                                    string,
                                    '</sup>'),
                                    y = 0.95, x = 0.5, xanchor = 'center', yanchor =  'top'))

layout(title = list(text='Plot Title', y = 0.95, x = 0.5, xanchor = 'center', yanchor =  'top'))
string <- "test"

"Note: not all values are denominated in the same currency"
```

@@

ordinaert_p_met <- kreft_html |> 
  mutate(
    profit = ifelse(ordinaert_resultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, ordinaert_resultat, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  theme(legend.position = "none") +
  scale_fill_met_d("Tsimshian",
                   direction = ifelse(mean(kreft_html$ordinaert_resultat) == 1,-1, 1)) +
  theme(legend.position = "none") +
  labs(x = "", y = "")
ggplotly(ordinaert_p_met)

# function extracted

  # Reactive function to check for currency and use an appropriate subtitle
  currency_subtitle <- reactive({
    if (length(unique(htmldata()$valutakode)) == 1){
      ""
    } else {
      "Note: not all values are denominated in the same currency"
    }
  })
```

@@

kreft_html_with_variables |> 
  ggplot(aes(year, sum_egenkapital_og_gjeld, fill = balance_positive)) +
  geom_col() +
  currency_scale() +
  scale_fill_met_d("Tsimshian",
                   direction = ifelse(
                     mean(kreft_html_with_variables$balance_positive,
                          na.rm = TRUE) == 1,-1, 1)) +
  theme(legend.position = "none") +
  labs(x = "Year", y = "", title = "Balance (in thousands)",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(kreft_html_with_variables$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))

currency_scale <- function()
  {scale_y_continuous(
        # Checking for uniform currency code
        labels = ifelse(length(unique(kreft_html_with_variables$valutakode)) == 1,
          # Using the currency code if uniform
          label_dollar(prefix = str_c(kreft_html_with_variables$valutakode[1], " ")),
          # alternative prefix if multiple currencies in the data
          label_dollar(prefix = "? ")
        )
      )
  }
```

@@

kreft_excel |> mutate(
            KPI_admin =
              expenses_administrative / expenses_program_services *100) |> 
           filter(year == max(year)) |> 
          select(KPI_admin)

kreft_excel |>
      mutate(
        KPI_admin =
          str_c( # Using str_c() to concatenate value and % sign
            format( # shortening(lengthening) the resulting value
              # calculating the value
              (expenses_administrative / (expenses_program_services +
                                            expenses_administrative +
                                            expenses_fundraising +
                                            expenses_other) * 100),
              digits = 3
            ), "%"
          )
      ) |>
      filter(year == max(year)) |> # selecting latest available year
      select(KPI_admin) |> # dropping all other variables
      str_flatten() # turning into a single string

kreft_excel |>
      mutate(
        KPI_admin =
            format( # shortening(lengthening) the resulting value
              # calculating the value
              (expenses_administrative / (expenses_program_services +
                                            expenses_administrative +
                                            expenses_fundraising +
                                            expenses_other) * 100),
              digits = 3)
      ) |>
      filter(year == max(year)) |> # selecting latest available year
      select(KPI_admin) |> # dropping all other variables
      pull
  class()

KPI_admin_num <- kreft_excel |> 
  filter(year == max(year)) |> 
  transmute(
    KPI_admin = expenses_administrative / (expenses_program_services +
                                            expenses_administrative +
                                            expenses_fundraising +
                                            expenses_other) * 100
  ) |> 
  pull()

KPI_to_string <- function(variable){
  if (variable == 0 | is.na(variable)){
    NA
  } else {
    str_c(format(variable, digits = 3), "%")
  }
}

KPI_to_string(KPI_admin_num)
